% LaTeX resume using res.cls
\documentclass[line, 12pt]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newcommand\GPAindent[1][1cm]{\hspace*{#1}}
\newcommand\tab[1][0.5cm]{\hspace*{#1}}
\newcommand\skillsAndKnowledgeTab[1][4.6cm]{\hspace*{#1}}

%\usepackage[margin=0.75in]{geometry}

\usepackage[top=.25in, bottom=.25in, left=.25in, right=.75in]{geometry}
\begin{document}

\name{Mitchell J. Dzurick}

\address{\parbox{0.5\linewidth}{%
		\null\hfill mitchdz@email.arizona.edu	\\
		\null\hfill (520)-400-9183 \\
		\null\hfill dzurick.org
	}
}

\begin{resume}
%\section{OBJECTIVE}       
 
\section{EDUCATION} 
                {\sl M.S. Electrical \& Computer Engineering}
				$\mid$ \textbf{University of Arizona} \hfill Fall 2019 - \textbf{Spring 2021}\\
				\tab - Enrolled in Accelerated Masters Program. \\ 
				{\sl B.S. Electrical \& Computer Engineering}
                $\mid$ \textbf{University of Arizona} \hfill Spring 2020\\
                \GPAindent GPA: \textbf{3.784}/4.00 \\
                {\sl Member} $\mid$ \textbf{Eta Kappa Nu IEEE}
                	\hfill Spring 2018 - Present \\
                \tab - Awarded to top 25\% of 2nd semester Sophomores. \\
                {\sl Dean's List} $\mid$ \textbf{University of Arizona College of Engineering} \hfill Fall 2016 - 2020 \\
                \tab - Award for academic distinction throughout the school year.


\section{EXPERIENCE} 
				{\sl Software Security Engineer} $\mid$ \textbf{Intel Corporation} \hfill Summer 2019 - Present \\
				\tab - Integrated automated unit testing framework into legacy C library, with plans to open source.\\
				\tab - Developed multiple Yocto bitbake layers that will be used on various IOT and consumer devices. \\
				\tab - Code owner of project that discovers security solutions on the platform in real time. 
												
				{\sl Student Project} $\mid$ \textbf{University of Arizona Computer Architecture}\hfill Fall 2018 \\
				%\begin{itemize}  \itemsep -2pt %reduce space between items
				\tab - Constructed a general purpose pipe-lined processor that runs 32 bits MIPS. \\
				\tab - Created a Datapath that utilizes full-forwarding \& hazard detection components. \\
				\tab - Introduced Branch Prediction \& Speculative Execution. 
				%\end{itemize}	
				
				{\sl Software Security Engineer} $\mid$ \textbf{Intel Corporation} \hfill Summer 2018 \\
                \tab - Analyzed large datasets using an Artificial Neural Network. \\
                \tab - Created embedded Linux distributions with Yocto Project.\\
                \tab - Developed simple Intel Software Guard eXtension program.
 		
 
                {\sl Lab Assistant} $\mid$ \textbf{University of Arizona Computer Programming II}\hfill Spring 2018 \\
                 %\begin{itemize}  \itemsep -2pt %reduce space between items
                 	\tab - Provided Office Hours to help students with C++ programming. \\
                 	\tab - Projects have time constraints that require algorithm optimization.
                 %\end{itemize} 
				
				
				

\section{INVOLVEMENT} 
	Vice President $\mid$ \textbf{University of Arizona H.A.C.K.S} \hfill Summer 2017 - Summer 2020 \\
	\tab - Use Proxmox VE hypervisor to create and manage multiple virtual machines. \\
	\tab - Teach system administration and Cyber Security.

	Vice Chair $\mid$ \textbf{University of Arizona IEEE} \hfill Summer 2018 - Summer 2020 \\
		\tab - Gain social skills in a professional environment in order to benefit the student organization. \\
		\tab - Organize and teach a soldering workshop for the Microcontroller Design class.
	

\section{SKILLS \& KNOWLEDGE} 
	- {\sl Languages \& Software:} C, C++, Bash Scripting, Bitbake, Yocto, Python, Java, Matlab, Verilog, \\ \tab[4.48cm] basic x86 \& MIPS Assembly, qtspim, Javascript, HTML. \\ \\
	- {\sl Technical Skills:} Operating Unix machines, Basic Linux Binary Analysis, Program Debugging, \\ \tab[3.25cm] Test Driven Design, Basic Circuit Analysis, Soldering, git.
 

\end{resume}
\end{document}







