% LaTeX resume using res.cls
\documentclass[line, 12pt]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newcommand\GPAindent[1][1cm]{\hspace*{#1}}
\newcommand\tab[1][0.5cm]{\hspace*{#1}}
\newcommand\skillsAndKnowledgeTab[1][4.6cm]{\hspace*{#1}}

%\usepackage[margin=0.75in]{geometry}

\usepackage[top=.25in, bottom=.25in, left=.25in, right=.75in]{geometry}

\begin{document}

\name{Mitchell J. Dzurick}

\address{\parbox{0.5\linewidth}{%
		\null\hfill mitchdz@email.arizona.edu	\\
		\null\hfill linkedin.com/in/dzurick \\
		\null\hfill (520)-400-9183
	}
}

\begin{resume}
%\section{OBJECTIVE}       
 
\section{EDUCATION} 
				{\sl B.S. Electrical \& Computer Engineering}
                % \sl will be bold italic in New Century Schoolbook (or
	        	% any postscript font) and just slanted in
				% Computer Modern (default) font
                $\mid$ \textbf{University of Arizona} \hfill Fall 2016 - Spring 2020\\
                \GPAindent GPA: \textbf{3.667}/4.00 \\
                {\sl Member} $\mid$ \textbf{Eta Kappa Nu IEEE}
                	\hfill Spring 2018 - Present \\
                \tab - Awarded to top 25\% of 2nd semester Sophomores. \\
                {\sl Dean's List} $\mid$ \textbf{University of Arizona College of Engineering} \hfill Fall 2016 - 2017 \\
                \tab - Award for Academic Distinction throughout the 2016 school year.


\section{EXPERIENCE} 
				
				{\sl Student} $\mid$ \textbf{University of Arizona Computer Architecture}\hfill Fall 2018 - Current \\
				%\begin{itemize}  \itemsep -2pt %reduce space between items
				\tab - Constructing 32 bit general purpose pipe-lined processor that runs 32 bits MIPS. \\
				\tab - Datapath utilizes full-forwarding \& hazard detection components. \\
				\tab - Introduces Branch Prediction \& Speculative Execution. \\
				\tab - Plan to implement Vector Processing Unit.
				%\end{itemize} 
				
				
				
				{\sl Software Security Engineer} $\mid$ \textbf{Intel Corporation} \hfill Summer 2018 \\
                 	\tab - Analyze large datasets using an Artificial Neural Network. \\
                 	\tab - Create embedded Linux distributions with Yocto Project. \\
                 	\tab - Develop simple Intel Software Guard eXtension program.
 		
 				%\begin{itemize}  \itemsep -2pt % reduce space between items
 				%	\item Analyze large datasets using an Artificial Neural Network.
 				%	\item Create embedded Linux distributions with Yocto Project.
 				%	\item Develop simple Intel Software Guard eXtension program.
 				%\end{itemize}
 
                {\sl Lab Assistant} $\mid$ \textbf{University of Arizona Computer Programming II}\hfill Spring 2018 \\
                 %\begin{itemize}  \itemsep -2pt %reduce space between items
                 	\tab - Provide Office Hours to help students with C++ programming. \\
                 	\tab - Requires knowledge of data structures and algorithms. \\
                 	\tab - Projects have time constraints that require algorithm optimization.
                 %\end{itemize} 


				{\sl Student} $\mid$ \textbf{University of Arizona Digital Logic}\hfill Fall 2017 \\
					%\begin{itemize}  \itemsep -2pt %reduce space between items
						\tab - Constructed a 32-bit single cycle processor in Verilog. \\
						\tab - Ran simulation of a processor on a Nexys 4 DDR Artix-7 FPGA board.
				%\end{itemize} 
				
				
				

\section{INVOLVEMENT} 
	Chair $\mid$ \textbf{University of Arizona IEEE} \hfill Summer 2018 - Present \\
		\tab - Gain social skills in a professional environment in order to benefit the student organization. \\
		\tab - Organize and teach a soldering workshop for the Microcontroller Design class.
	
	Vice President $\mid$ \textbf{University of Arizona H.A.C.K.S} \hfill Summer 2017 - Present \\
		\tab - Use Proxmox VE hypervisor to create and manage multiple virtual machines. \\
		\tab - Teach system administration and Cyber Security.

\section{SKILLS \& KNOWLEDGE} 
	- {\sl Languages \& Software:} C, C++, Bash Scripting, Python, Java, Matlab, Verilog, \\ \tab[4.48cm] basic x86 \& MIPS Assembly, qtspim, UML, git. \\ \\
	- {\sl Technical Skills:} Operating Unix machines, Basic Linux Binary Analysis, Program Debugging, \\ \tab[3.25cm] Basic Circuit Analysis, Soldering.
 

\end{resume}
\end{document}







